Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-10 prop_iop.tex
prop_iop.tex Went through the Guildline...

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. Despite the fact that classically a IVPM could always
correspond to a real-valued probability measure, we found that there
may be no ``real'' infinitely-precise quantum state approximated
by a quantum IVPM as a whole. However, if a quantum IVPM is decomposed
into pieces, each piece might still be induced by a quantum state.
Moreover, our examples and Gleason's theorem summarized in table~\ref{table_long}
suggests that as the measurement resources increase, an entire quantum
IVPM could more and more likely be identified to a particular state.
\begin{table}[ht]
\center{%
\begin{tabular}{c|cccc}
Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
\hline 
Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $\frac{1}{2}$ & \ldots{} & $0$\tabularnewline
Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
Count of states correspond to pieces of $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
\hline 
How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
\end{tabular}}\caption{Relation between measurement resources and interval-valued probability
measures}
\label{table_long}
\end{table}
Additional work is in progress on the following research questions:
\begin{description}
\item [{Research Question.}] Confirm that there is always a quantum IVPM
with an empty-core if the length of the intervals is bigger than zero. 
\item [{Research Question.}] Find a general method to determine how a
quantum IVPM is close to the Born rule. 
\item [{Research Question.}] Confirm that as the number and precision
of the intervals increase the quantum IVPM converges to the measure
induced by the Born rule. 
\item [{Research Question.}] Investigate the status of the theorems of
Bell and Kochen-Specker for quantum IVPM.
\end{description}
Although we discussed how a quantum IVPM could be induced from a real
quantum state, our investigation leaves an open question of whether
there exists a ``real'' entity that exists independently of measurements
and probabilities. The possibility of no ``real'' underlying state
is consistent with the elegantly recent work on Quantum Bayesianism
or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which suggests
that the quantum state is more like an interactive system in computer
science parlance. In another word, the quantum state is subjective:
each observer has a different view of the quantum system that is consistent
with their previous observations and that allows that observer, independently
of other observers, to assign beliefs (i.e., probabilities) to possible
future interactions.

>>>>

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. Despite the fact that classically a IVPM could always
correspond to a real-valued probability measure, we found that there
may be no ``real'' infinitely-precise quantum state approximated
by a quantum IVPM as a whole. However, if a quantum IVPM is decomposed
into pieces, each piece might still be induced by a quantum state.
Moreover, our examples and Gleason's theorem summarized in table~\ref{table_long}
suggests that as the measurement resources increase, an entire quantum
IVPM could more and more likely be identified to a particular state.
\begin{table}
\caption{\label{table_long}Relation between measurement resources and
interval-valued probability measures.}
\begin{indented}
\item[]\begin{tabular}{c|cccc}
\br
Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
\mr
Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $\frac{1}{2}$ & \ldots{} & $0$\tabularnewline
Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
Count of states correspond to pieces of $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
\mr
How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
\br
\end{tabular}
\end{indented}
\end{table}
Additional work is in progress on the following research questions:
\begin{description}
\item [{Research Question.}] Confirm that there is always a quantum IVPM
with an empty-core if the length of the intervals is bigger than zero. 
\item [{Research Question.}] Find a general method to determine how a
quantum IVPM is close to the Born rule. 
\item [{Research Question.}] Confirm that as the number and precision
of the intervals increase the quantum IVPM converges to the measure
induced by the Born rule. 
\item [{Research Question.}] Investigate the status of the theorems of
Bell and Kochen-Specker for quantum IVPM.
\end{description}
Although we discussed how a quantum IVPM could be induced from a real
quantum state, our investigation leaves an open question of whether
there exists a ``real'' entity that exists independently of measurements
and probabilities. The possibility of no ``real'' underlying state
is consistent with the elegantly recent work on Quantum Bayesianism
or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012}, which suggests
that the quantum state is more like an interactive system in computer
science parlance. In another word, the quantum state is subjective:
each observer has a different view of the quantum system that is consistent
with their previous observations and that allows that observer, independently
of other observers, to assign beliefs (i.e., probabilities) to possible
future interactions.
